Constructing the transition graphs of interacting hysterons

### 2022-07-14 Paper_draft.tex
Added figure to show base graphs for single main loop & GoE pruning

\begin{table}[h!]
\begin{tabular}{l|l|ll|ll|}

@@

                                        &  & \multicolumn{2}{l|}{}    & \multicolumn{2}{l|}{}    \\ \hline
\multicolumn{1}{|l|}{}                  &  & \multicolumn{1}{l|}{} &  & \multicolumn{1}{l|}{} &  \\ \hline
\multicolumn{1}{|l|}{\multirow{2}{*}{}} &  & \multicolumn{1}{l|}{} &  & \multicolumn{1}{l|}{} &  \\ \cline{2-6} 
\multicolumn{1}{|l|}{}                  &  & \multicolumn{1}{l|}{} &  & \multicolumn{1}{l|}{} &  \\ \hline
\multicolumn{1}{|l|}{\multirow{2}{*}{}} &  & \multicolumn{1}{l|}{} &  & \multicolumn{1}{l|}{} &  \\ \cline{2-6} 
\multicolumn{1}{|l|}{}                  &  & \multicolumn{1}{l|}{} &  & \multicolumn{1}{l|}{} &  \\ \hline

@@

\end{table}

>>>>

\begin{tabular}{c|c|cc|cc|}

@@

                                        & 100, up & \multicolumn{2}{c|}{3}    & \multicolumn{2}{c|}{2}    \\ \hline
\multicolumn{1}{|c|}{110, down}                  & \backslashbox{101,  down}{010,  up} & \multicolumn{1}{c|}{3} &  1& \multicolumn{1}{c|}{3} &  1\\ \hline
\multicolumn{1}{|c|}{\multirow{2}{*}{1}} &  1& \multicolumn{1}{c|}{ \includegraphics[width=0.08\textwidth]{14-07-2022_N3graphs_ML132/graph10.pdf}} &  \includegraphics[width=0.08\textwidth]{14-07-2022_N3graphs_ML132/graph2.pdf} & \multicolumn{1}{c|}{ \includegraphics[width=0.08\textwidth]{14-07-2022_N3graphs_ML132/graph8.pdf}} &    \includegraphics[width=0.08\textwidth]{14-07-2022_N3graphs_ML132/graph0.pdf}\\ \cline{2-6} 
\multicolumn{1}{|c|}{}                  &  3& \multicolumn{1}{c|}{ \includegraphics[width=0.08\textwidth]{14-07-2022_N3graphs_ML132/graph14.pdf}} &   \includegraphics[width=0.08\textwidth]{14-07-2022_N3graphs_ML132/graph6.pdf}& \multicolumn{1}{c|}{ \includegraphics[width=0.08\textwidth]{14-07-2022_N3graphs_ML132/graph12.pdf}} &  \includegraphics[width=0.08\textwidth]{14-07-2022_N3graphs_ML132/graph4.pdf}\\ \hline
\multicolumn{1}{|c|}{\multirow{2}{*}{2}} &  1& \multicolumn{1}{c|}{ \includegraphics[width=0.08\textwidth]{14-07-2022_N3graphs_ML132/graph11.pdf}} &  \includegraphics[width=0.08\textwidth]{14-07-2022_N3graphs_ML132/graph3.pdf} & \multicolumn{1}{c|}{ \includegraphics[width=0.08\textwidth]{14-07-2022_N3graphs_ML132/graph9.pdf}} &   \includegraphics[width=0.08\textwidth]{14-07-2022_N3graphs_ML132/graph1.pdf}\\ \cline{2-6} 
\multicolumn{1}{|c|}{}                  &  3& \multicolumn{1}{c|}{ \includegraphics[width=0.08\textwidth]{14-07-2022_N3graphs_ML132/graph15.pdf}} &  \includegraphics[width=0.08\textwidth]{14-07-2022_N3graphs_ML132/graph7.pdf} & \multicolumn{1}{c|}{ \includegraphics[width=0.08\textwidth]{14-07-2022_N3graphs_ML132/graph13.pdf}} &   \includegraphics[width=0.08\textwidth]{14-07-2022_N3graphs_ML132/graph5.pdf}\\ \hline

@@

\caption{All sixteen base graphs for the example main loop (1, 3, 2). GoE pruning reduces the number of distinct base graphs from sixteen to four, out of which three are solvable in the linear model. \note{NO REFERENCE TO THIS FIG}}
\label{fig:goepruning}
